Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2018-12-13 manuscript/reply_to_referees.tex

\documentclass[12pt]{letter}

\usepackage[britdate]{LiU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\begin{document}

\newpage

\setcounter{page}{1}

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Referee \#1}
% ---------------------------------------

  Referee 1 focused their critique entirely on our methods. They were concerned that our novel approach had not been properly validated or compared to previous methods, and that we did not have within-family resolution for our tree. We respond (preceded by \textbf{R:}) to each of these concerns in detail below.

  1. Request for statistical validation

    \begin{refquote}

      I think that the introduction of a new method should be validated in terms of statistical power (type I and II error) ... For example, how the new method accounts for the non-independent use of the same species in different pairwise interactions?

    \end{refquote}

    \textbf{R:} Solution was something to do with making >100 simulations of each empirical network and then >100 simulations of each simulation...

  2. Request for comparison with other methods

    \begin{refquote}

      I think that the introduction of a new method should be ... compared with existing methods.  Does the new method outperforms  those of Ives \& Godfray (2006, Am Nat 168),  Rafferty and Ives (2013, Ecology 94) or Hadfield et al (2014, Am Nat 183)? The latter method identifies three sources of phylogenetic signal: host/parasite specialism-generalism, host/parasite evolutionary interactions, and the coevolutionary interaction. Can the new method identify these sources of phylogenetic signal between plants and animals (pollinators or herbivores)?

    \end{refquote}

    \textbf{R:} I need to re-read these papers. As I recall, they were asking slightly different questions but I didn't fully understand their methodologies.

      %     Our study and those that the author mention are designed to answer different
      % questions. Ives \& Godfray (2006) developed their method to ask whether a
      % plant (or the majority of plants in a community) is visited by a related set of 
      % pollinators (and vice versa). We are interested in whether related plants are 
      % visited by similar sets of pollinators, regardless of whether or not the 
      % pollinators are related. It is not obvious how to translate the results of their 
      % method (e.g., individual species of pollinators tend to visit related sets of plants) 
      % to our question, as two closely-related plants might be visited by non-overlapping 
      % sets of pollinators which nevertheless tend to visit related plants. This could 
      % occur, for example, if plants within a particular genus grow either in the 
      % understory or in more open microhabitats and each pollinator visits only plants of 
      % this genus that grow within its preferred microhabitat.

      % Similarly, Rafferty \& Ives (2013) used two phylogenetic linear
      % mixed models (PLMM's) to model the strength of plant-pollinator
      % interactions as a function of 1) plant traits and pollinator
      % phylogeny; and 2) plant and pollinator phylogenies. We were instead
      % interested in modelling plants' traits (i.e., their interaction
      % partners) over their phylogeny. In our case, we did not have pollinator
      % phylogenies and our `trait' of interest was the set of animals with
      % which a plant interacts. In Rafferty \& Ives' first PLMM, then, we
      % would need to include network structure as both a dependent and the
      % independent variable, while in the second we would be obliged to assume
      % that the pollinator phylogenies were completely uninformative. This is
      % almost certainly not the case. More importantly, even if we accept this
      % limitation and model the strength (or in our case, binary presence or 
      % absence) of interactions purely based on the plant phylogeny, it is not
      % clear how this model would allow us to assess whether or not plants 
      % tend to interact with similar \emph{sets} of animals. That is, we are not
      % interested in whether each particular animal has similar probabilities
      % of interacting with closely-related plants but rather in the amount of
      % overlap in the sets of animals that visit related and unrelated plants.

      % Hadfield \emph{et. al.}'s 2014 study addresses questions that are even
      % further from our study's focus. The authors of that study are mainly
      % interested in the interplay of two phylogenies (also a focus of
      % Rafferty \& Ives, 2013, but to a lesser degree). In our datset, we
      % had access to phylogenies for the plants but not their animal interaction
      % partners. As such, the referee is correct in noting that we do not 
      % identify sources of phylogenetic signal \emph{a la} Hadfield \emph{et. al.}.
      % In our study, we cannot test for co-evolution of plants and their 
      % partners or for other forms of evolutionary interaction between them. 
      % Without being able to eliminate these possibilities, testing for an 
      % effect of animal or plant specialism on interaction patterns tells us
      % little about the effect of plants' evolutionary histories.

      % [[We have edited the main text to make our question of interest (and
      % the ways in which it differs from the questions asked by other 
      % researchers) clearer. We have also added tests for type I and type II
      % statistical errors, as described below. We hope that this will provide
      % a sufficient indication of the quality of our method, as we cannot 
      % in good concience compare our results to those of methods asking different
      % questions.]]

  3. Between-family resolution is not sufficient

    \begin{refquote}

      Regarding the phylogenetic patterns within plant families, I am afraid that the authors do not have neither topological nor cronological resolution in the phylogenetic tree to run these analyses. The topology provided by phylomatic is resolved at the family level, and then it may produce a lot of polytomies at the genus and species level. Similarly, Wilkstrom et al's calibration points are not enough to calibrate divergence points within families. Instead, the authors use the bladj algorithm, which distribute the undated nodes following a mathematical function which is strongly dependent on the number of tips in that particular clade.  Bladj + Wikstrom ages may work well to detect patterns at the community level where phylogenetic distances among species from different clades are averaged.  However, when phylogenetic distances within lower taxonomic entities (families, genera) are needed, a more accurate calibration is needed. Otherwise, phylogenetic distance is confounded with species richness within clades (i.e. the phylogenetic distance between two species of a family will depend on the  number of species in that family and not on the true phylogenetic distance among them). For that reason, I have serious doubts about the phylogenetic patterns within families shown by the authors. Accurate chronograms at genus and species level would be necessary to extract robust conclusions.

      \end{refquote}

      \textbf{R:} We accept the author's reluctance to accept conclusions based on Bladj + Wikstrom age dates. As none of the authors of this manuscript has any expertise relevant to constructing chronograms, however, we are strictly limited to using published dates of divergence between taxa. Fortunately, while this manuscript was being revised a recent dated tree (that of Zanne \emph{et al.}, 2014) has been incorporated into the Phylomatic web tool. We have rebuilt our dated trees using this phlogeny, which incorporates within-family divisions. We hope that this additional detail will satisfy the reviewer.

\section*{Referee 2}

  Referee 2 was very positive about our manuscript and only had a few minor suggestions. We thank the Referee for her thoughtful input.

  1. Expand the title

    \begin{refquote}

      I think the title could be improved to bring a "bigger message" (which is in the manuscript), such as stressing the great spatial extent of the study. E.g. Global assessment of plant-pollinator-herbivore evolutionary interactions reveals great variation across communities and plant families, etc.

    \end{refquote}

    \textbf{R:} Assuming this still fits after re-analysis, seems like a good idea.

  2. Add more evolutionary/community-ecology context

    \begin{refquote}

      I also think it would be very interesting to put this work in a context of evolutionary community ecology, in order to potentially understand the evolutionary development of the traits in the plant families studied in this work. Specifically, it would be worth testing the study system in the framework of specialist vs. generalist herbivores and specialist vs. generalist pollinators. Taking into consideration that herbivores and pollinators have an evolutionary contrasting impact on plants: plants want to escape herbivores but want to be pollinated. So we can guess that being a specialist herbivore might have an opposite effect than being a specialist pollinator: we might find more distantly related species co-existing in plant communities where specialist herbivores dominate; and more closely related co-existing plant species when generalist herbivores dominate. Contrastingly, in the presence of specialist pollinators, co-existing plants are closely related. Whereas plant are distantly related when generalist pollinators dominate. These community-levels works might be interesting:

      \smallskip

      Yguel, B., Bailey, R., Tosh, N. D., Vialatte, A., Vasseur, C., Vitrac, X., ... \& Prinzing, A. (2011). Phytophagy on phylogenetically isolated trees: why hosts should escape their relatives. Ecology Letters, 14(11), 1117-1124.
      \smallskip
      Castagneyrol, B., Jactel, H., Vacher, C., Brockerhoff, E. G., \& Koricheva, J. (2014). Effects of plant phylogenetic diversity on  herbivory depend on herbivore specialization. Journal of Applied Ecology, 51(1), 134-141.
      \smallskip
      Yguel, B., Bailey, R. I., Villemant, C., Brault, A., Jactel, H., \& Prinzing, A. (2014). Insect herbivores should follow plants escaping their relatives. Oecologia, 176(2), 521-532.

      \end{refquote}

    \textbf{R:}

\section*{Referee 3}

  Referee 3 saw "the potential [[for our study]] to become a significant contribution to the field of ecological networks" if a number of significant issues are addressed. Specifically, the Referee found several sections to be unclear, the discussion to be shallow, and lacked confidence in our statistical analyses. We address each point below and hope that our responses (preceded by \textbf{R:}) will satisfy the Referee.

  1. Use randomization tests to address non-independence of pairs of species

    \begin{refquote}

      If I understood right the authors used the paired niche overlap and the shared evolutionary history of each pair of species as data points in their analyses. However, pairs of species are not independent. I am not here worried about the evolutionary dependence of pairs of species. Rather, I am worried that in a network with P plant species, each plant species will participate of P-1 data points. These data points, as a consequence, are not independent and the authors need to incorporate this dependency in their analysis. A simple way of circumvent this problem is to use randomization tests to build up an empirical distribution for the metric of interest in the presence of the dependency of data points.

      \end{refquote}

      \textbf{R:}

  2. Demand for more detailed discussion of system-specific biology

    \begin{refquote}

      One of the main weaknesses of the manuscript is that the huge amount of information we know about plant-insect interactions in the wild is ignored in the methods section and the discussion of the paper. Examples include:

      \begin{itemize}

      \item Line 77. The authors carefully restricted their herbivore dataset to only those insects that feed on leaves. Having said that, inspecting their dataset it is possible to notice that distinct herbivory networks are formed by distinct groups of insects such as grasshoppers, lepidopterans, and leaf beetles. We know for a long time these herbivores markedly vary in the way they interact with plants. As a result, networks formed by these herbivores and their host plants are very distinct, varying in many network structural patterns (Pires and Guimares 2013. Interface). I missed a deeper discussion on the role of biological traits (often mentioned in the vague "traits" way) in shaping network patterns. For example, physical and physiological integration associated with interaction intimacy might explain the stronger "phylogenetic effect" observed in herbivory networks that involve leaf beetles and lepidopterans.

      \item There is a lot of information on plant families that are known to have secondary metabolites that deter multiple herbivores. Along the same lines, there is a lot of information on flower morphology that constrains or favors particular types of pollinators. Flower morphology, in turn, is often a family-level attribute. Nevertheless, there is no attempt of relate the patterns the authors observe with the solid body of information on the biology of plant-insect interactions.

      \item Lines 238-248 and 339-341. Which is the biological meaning of the fact the families associated to networks with steepest relationships between niche overlap and shared evolutionary history did not show steep relationships between niche overlap and shared evolutionary history? It is not clear to me.

      \item In the discussion the authors hypothesize that pollinator syndromes would be more common within families with weaker evidence of effects of shared evolutionary history. However, twenty years ago Jordano (1995. AmNat) showed that syndromes – at least in seed dispersal systems – are associated with shared evolutionary history. Thus, there is no reason to assume that syndromes are more likely to occur in interactions in which shared evolutionary history has an weaker association on patterns of interaction.

    \end{itemize}
    \end{refquote}

    \textbf{R:} We hope that the Referee appreciates the fact that length restrictions limit our ability to go into too much detail in the Discussion without severely compromising our explanation of the methods. Nevertheless, where possible we have added biological details throughout the manuscript. We have taken particular care to address the specific points the Referee has highlighted above.

  3. Request to provide more detail about specialist pollinators

    \begin{refquote}

      It is puzzling that pollinators show smaller number of interactions than herbivores. It is the opposite of all we know about herbivory and plant-pollinator interactions. It might be a consequence of lumped grasshoppers with other herbivores, the effect of analyzing occasional flower visitors as specialists in pollinator networks, or a consequence of poor sampling in pollinator networks. I would like the authors to provide more information on which are those "pollinator specialists" and on how exhaustive is the sampling of the networks they analyze.

    \end{refquote}

    \textbf{R:} As we used published networks rather than collecting data ourselves, we cannot provide information on the exhaustiveness of sampling other than that given in the original sources (detailed in the SI). In particular, we cannot say which apparently specialist pollinators appear specialized because of rarity and which are genuinely specialized as data on abundances were not published together with the bulk of the metworks we used. The questions the Referee asks about the adequacy of sampling and specialization in plant-pollinator networks are very important, but we respectfully suggest that they are best addressed by encouraging empirical researchers to publish abundance data as well as interaction networks. There is very little we can do to address these questions when re-analysing the limited data that have been made available.

   One thing we can do, however, is investigate the effects of lumping grasshoppers in with other herbivores. To that end, we have repeated our analyses excluding the plant-herbivore networks which contained grasshoppers. As removing these networks substantially reduces our already small collection of plant-herbivore networks, we retain these networks in the main text and present the re-analysis in the SI. [[What changed?]]

 4. Demand for further clarification of the methods

    \begin{refquote}

      Some methodological approaches are not clear and becase of that it would be impossible to replicate this study.

        \begin{itemize}
          \item Line 113-115. Why? Please explain.
          \item Line 122-125. How this difference is incorporated in the analysis? It is not clear. Differences between the two cases would not lead to an undesirable effect of generalism on your metric?
        \end{itemize}

      \end{refquote}

      \textbf{R:} We appreciate the Referee's frankness.

  5. The null model approach is confusing

    \begin{refquote}

      The null model approach (Lines 163-170) makes no sense for me. The authors permutate species between networks of a given type but not between networks of different types. Why? Plants that are animal-pollinated can be attacked by herbivores and animals pollinate many plants attacked by herbivores. In contrast, the authors randomize species from pollinator networks that are occuring in distinct biogeographical regions. I understand that in such kind of broad scale study we need to simplify the use of biological information, but a really robust approach would control for non-sense geographical swaps (e.g., among distinct continents) and to prevent the swap that place plants that are not pollinated by animals in pollinator networks but otherwise would allow that plant species to be swaped between network types.

      \end{refquote}

      \textbf{R:}

  6. Request for dated clades

    \begin{refquote}

      Lines 94-96. "These dates included divergence times in millions of years (My) between families and within some families, but did not give dates for divergences within genera". Please provide the dated clades.

      \end{refquote}

      \textbf{R:} The dated clades used in our original analyses are those given by Wikstrom \emph{et al.} ([[year]]). We have since re-created our analyses using the dated tree given in Zanne \emph{et al.} (2014) as found in the Phylomatic web application. We do not have separate dated clades for specific taxa. As both of these clades have already been published, repeating them in our manuscript would be purely redundant.

  7. The Referee is confused

    \begin{refquote}

      Some sentences are just hard to follow and/or are puzzling. Exemples include but are not limited to: "These relationships were also significantly related to the composition of the network’s plant component", "plants that produce noxious secondary metabolites may suffer fewer herbivores", "Interestingly, in our analyses the plant families associated with the steepest relationships between niche overlap and phylogenetic distance at the network level did not show particularly steep relationships within themselves".

    \end{refquote}

    \textbf{R:} We do not understand why the Referee finds some of the above examples confusing, particularly "plants that produce noxious secondary metabolites may suffer fewer herbivores". We have nevertheless rephrased the cited examples and revised our manuscript for clarity. This request for simpler phrasing often comes at the cost of brevity, which unfortanately makes it very difficult to comply with the Referee's demand for more biological detail (point 2). We hope that we have struck a reasonable balance between these two criticisms.

  8. The Referee hates our conclusion

    \begin{refquote}

      Line 331. "This may be because pairing antagonistic and mutualistic interactions balances the indirect effects of these interactions, leading to a more stable community (Sauve et al., 2014)". The attempt of explain patterns of interaction that are mold by selection acting on individuals and shaping populations in terms of advantages for the community makes no sense in the light of what we known about evolutionary biology and ecological communities, which are transient aggregations of coexisting species that show no clear boundaries in either space or time and from which there is little evidence of heritability in traits.

      \end{refquote}

      \textbf{R:} We are confused by the Referee's argument that communities show no clear boundaries in either space or time and that there is little evidence of heritability in traits within a community. This seems to suggest that the Referee does not believe in ecological communities or networks as viable units of study or in evolution (which requires heritability of traits). If this is so, then the Referee is not an appropriate reviewer for this manuscript. We instead hope that the Referee is attempting to make the point that communities are not shaped for the benefit of the species within them and simply doing so in an unclear way. That being the case, of course we are aware of this and agree 100\%. We did not intend to suggest that either species are selected to stabilize their communities or that communities are selected to maintain the species within them. We are well aware of spatial and temporal turnover, and of the fact that most communities are not at equilibrium and therefore we should not expect network structure to remain constant. Our point was rather that a more stable community is likely to persist longer than a less stable community and, therefore, more likely to be observed. We therefore expect communities with patterns of interactions condusive to long-term persistence to be over-represented in the empirical networks available to us. We have revised and expanded our conclusion to explicitly state that we are \textbf{not} suggesting any kind of community-level selection process, only the disproportionate change of unstable communities to more stable ones. We hope that this revision is less objectionable to the Referee.

\end{document}

### 2018-12-13 manuscript/phylogenetic_signal_manuscript.tex
adding code and ms

  We studied phylogenetic conservation of interactions within a 
  set of 59 pollination and 11 herbivory networks. 
  These networks span a range of biomes 
  (desert to scrub forest to grassland) and countries (Sweden to 
  Australia), and range in size between 18 and 996 total species 
  (mean 160.93, median 96) with seven to 131 plant species (mean 38.06, 
  median 28).
  To ensure that we were analysing interactions influenced by similar
  sets of traits across networks, we restricted our herbivory 
  networks to insects consuming leaves. This excluded sap-sucking, 
  leaf-mining, and galling insects as well as seed predators and
  xylophagous insects; all of these interactions involve different 
  plant tissues and means of feeding
  than leaf consumption and so may be influenced by different
  plant and insect traits. We also excluded networks which focused on
  plants from a single genus as these did not contain sufficient
  variation in phylogenetic distance between plants.
  See \emph{Table S1, Supporting Information} for details on the original 
  sources of all networks.

@@

  We then estimated phylogenetic distances between species. To accomplish 
  this, we constructed a phylogenetic tree for our dataset based on the 
  phylomatic `mega-tree' of higher plants (version 20120829)~\citep{APG2009}. 
  Where possible, we dated nodes on the mega-tree according to~\citet{Wikstrom2001}. 
  These dates included divergence times in millions of years (My) between families and 
  within some families, but did not give dates for divergences within genera. For those
  nodes that were not included in the mega-tree, we used the branch length adjustment
  algorithm bladj~\citep{Webb2008} to estimate the ages of all undated nodes. This 
  means that the ages in our phylogenies are approximations, but the presence of 
  even a subset of properly dated nodes within a phylogeny improves upon undated, purely
  taxonomic approaches~\citep{Webb2000}. To obtain trees for each network, we 
  pruned the dated mega-tree to include only species in that network.

@@

  To fully describe the extent to which two plants' niches overlap,
  we defined the overlap between two plants' sets of interaction partners
  by recording the frequencies with which pairs of animals (where each animal 
  interacted with at least one plant) fall into three unique patterns
  (Fig.~\ref{overlap_patterns}). In the first pattern, both plants interact 
  with both animals, indicating total overlap for that quartet. In the second pattern, one plant
  interacts with both animal partners while the other
  interacts with only one animal, indicating partial overlap. In the third pattern,
  each animal interacts with only one plant, indicating no overlap. 
  Taken together, the frequencies of these three patterns of
  overlap can be used to describe the degree to which two plants have
  similar interaction partners. %

  Using the three patterns defined above provides more detail than other measures of overlap,
  such as the proportion of one species' partners that are shared with
  another as given by Jaccard similarity. In particular, comparing the probability of observing each pattern
  rather than one of the other two provides a measure of indirect
  interactions between plants by considering pairs of animal partners rather
  than each animal separately. For example, a pair of plants which share 
  two interaction partners are more likely to influence each other via these partners
  than two plants which do not share interaction partners. Moreover, our measure
  of overlap has greater statistical power than Jaccard dissimilarity because
  it includes information on the \emph{number} of shared interaction partners as
  well as the proportion. For instance, a pair of plants which together interact
  with 100 animals provides more information about shared overlap than a pair of
  plants which together interact with only one animal whereas the Jaccard similarity
  of both would simply be one.

@@

  To determine how overlap of interaction partners
  breaks down over phylogenetic distance,
  we modelled the probabilities of observing each pattern
  of overlap relative to the other two patterns.
  We expected that the frequency of the high- and moderate-overlap 
  patterns would decrease with increasing phylogenetic distance
  between two plants while the frequency of the low-overlap pattern would
  increase. As we expect pollination and herbivory networks could 
  show different patterns of overlap, we included effects of network 
  type and the interaction between network type and distance. Lastly, to
  account for the possibility that different communities show different
  characteristic relationships, we also included random effects of network ID on the slope 
  and intercept, giving a mixed-effects logistic regression of the form
  \begin{equation}
  logit(\omega_{pnij}) \propto \delta_{ij} + \rho_{n} + \delta_{ij}\rho_{n} + N_{n} + \delta_{ij}N_{n} ,
  \label{networklevel}
  \end{equation}

  \noindent where $\omega_{pnij}$ is the probability of overlap pattern $p$ occurring between
  species $i$ and $j$ in network $n$, $\delta_{ij}$ is the phylogenetic distance between 
  plants $i$ and $j$, $\rho_{n}$ is the network type (one in pollination networks,
  zero in herbivory networks), and $N_n$ and $\delta_{ij}N_{n}$ are random slope and intercepts 
  for network $n$. All models were fit using R function glmer from package lme4~\citep{lme4}.
  Sample size for these models was the sum (over all pairs of plants) of the number of pairs 
  of animals where each plant and each animal has at least one interaction partner. Over all 
  networks, there were 43,288,090 such sets of plants and animals, with a median of 72 (mean 
  671 +/- 2247) pairs of animals per pair of plants and median 58,528 (mean 636,590)
  plant-animal sets per network.

@@

  Next, we examined the connection between our network-level observations
  and the plant families present in each community.
  Specifically, we tested the hypothesis that
  varying relationships between phylogenetic distance and
  pairwise niche overlap are due to the different distributions 
  of families across networks. To do this, we performed a non-parametric
  permutational multi-variate analysis of variance
  (PERMANOVA;~\citealp{Anderson2001}) using the change in log
  odds of observing each pattern of overlap to 
  predict the Bray-Curtis dissimilarity of networks
  based on the composition of their plant component
  (defined as the proportions of the plant community
  made up by each plant family present in the entire dataset).
  We used Bray-Curtis dissimilarity because, for a given
  pair of networks, only those plant families that appear
  in at least one network are considered~\citep{Anderson2001,Cirtwill2015}; 
  that is, the absence of rare plant families will not make 
  two networks appear more similar than they actually are.

  Note that a PERMANOVA does not assume that the data are 
  normally distributed, but rather compares the pseudo-$F$ 
  statistic calculated from the observed data to a null 
  distribution obtained by permuting the raw data. As 
  pollination and herbivory networks might have different
  community composition and the change in log odds of observing
  different patterns of overlap, we stratified these permutations
  by network type. That is, the change in log odds for a pollination
  network could only be exchanged for that of another pollination
  network. Stratifying the permutations in this way ensures that 
  the null distribution used to calculate the $P$-value is not 
  biased by including combinations of changes in log odds and 
  community composition that would not occur because of inherent 
  differences in the two network types (e.g., \emph{Pinaceae} 
  only appeared in herbivory networks and should not be assigned 
  to pollination networks). We used 9999 such stratified permutations 
  to obtain the null distribution and obtain a $P$-value.

  The PERMANOVA tests whether there is an association between
  community composition and network-level patterns but does not
  give any information on \emph{which} plant families have the
  greatest effects. To address this, we supplemented the 
  PERMANOVA with three constrained correspondence analyses (CCAs)
  which placed plant families along an axis representing the
  change in log odds of observing each pattern of overlap.
  A correspondence 
  analysis (CA) is similar to other multivariate
  analyses such as principal components analysis in that it
  reduces multivariate data to a set of orthogonal axes. A
  subset of axes that explain the majority of variation in 
  the data can then be interpreted to elucidate trends that
  were difficult to interpret in the full multivariate space.
  A constrained correspondence analysis (CCA) creates an extra
  axis based on some constraint - in this case, the change in
  log odds of observing each pattern of overlap.

>>>>

  We studied phylogenetic conservation of interactions within a 
  set of 59 pollination and 11 herbivory networks. 
  These networks span a range of biomes 
  (desert to scrub forest to grassland) and countries (Sweden to 
  Australia), and range in size between 18 and 996 total species 
  (mean 160.93, median 96) with seven to 131 plant species (mean 38.06, 
  median 28).
  To ensure that we were analysing interactions influenced by similar
  sets of traits across networks, we restricted our herbivory 
  networks to insects consuming leaves. This excluded sap-sucking, 
  leaf-mining, and galling insects as well as seed predators and
  xylophagous insects; all of these interactions involve different 
  plant tissues and means of feeding
  than leaf consumption and so may be influenced by different
  plant and insect traits. The bulk of our herbivory networks 
  included only leaf-chewing insects. Where a network contained other
  types of herbivores we removed the non-leaf-chewing insects. Any
  plants which had no interaction partners after removing other types
  of herbivores were also removed. We also excluded networks which focused on
  plants from a single genus as these did not contain sufficient
  variation in phylogenetic distance between plants. This left us
  with a final data set of 54 pollination and 11 herbivory networks.
  See \emph{Table S1, Supporting Information} for details on the original 
  sources of all networks.

@@

  We then estimated phylogenetic distances between species. To accomplish 
  this, we constructed a phylogenetic tree for our dataset based on a dated
  `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
  in the angiosperm mega-tree (largely ferns and tree ferns). For angiosperms,
  a sister taxon was identified using~\citet{APW} and the species added manually.
  Ferns, tree ferns, and a single club moss were added to the base of the tree.
  This means that closely-related non-angiosperm species appear to have very long 
  phylogenetic distances between them. For this reason, we excluded comparisons 
  between pairs of non-angiosperms from our analyses. As only two networks (both 
  plant-herbivore networks) included more than one such species and non-angiosperms
  were always a small minority of any network, we do not 
  believe that omitting these comparisons has greatly affected our results.
  To obtain trees for each network, we 
  pruned the dated mega-tree to include only species in that network.

@@

  We calculated niche overlap for each pair of species within
  a community using a modified Jaccard index. The 
  Jaccard index $J_{ij}$ describes the proportion of shared interaction 
  partners for for species $i$ and $j$ and is defined as:

  \begin{equation}
    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_ij} ,,
  \end{equation}

  where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
  species $i$ and $j$ and $P_i$ and $P_j$ are the sets of interaction 
  \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
  weight to species sharing a large number of interaction partners as well as 
  those sharing a large proportion (i.e., to emphasize pairs of generalists 
  sharing most of their interaction partners over specialists sharing a single 
  interaction partner). We therefore recorded, for each species, the number of 
  shared interaction partners $M_{ij}$ and the number of interaction partners 
  that were not shared ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a 
  single index $J_{ij}$ we therefore defined niche overlap between species
  $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).

  % To fully describe the extent to which two plants' niches overlap,
  % we defined the overlap between two plants' sets of interaction partners
  % by recording the frequencies with which pairs of animals (where each animal 
  % interacted with at least one plant) fall into three unique patterns
  % (Fig.~\ref{overlap_patterns}). In the first pattern, both plants interact 
  % with both animals, indicating total overlap for that quartet. In the second pattern, one plant
  % interacts with both animal partners while the other
  % interacts with only one animal, indicating partial overlap. In the third pattern,
  % each animal interacts with only one plant, indicating no overlap. 
  % Taken together, the frequencies of these three patterns of
  % overlap can be used to describe the degree to which two plants have
  % similar interaction partners. %

  % Using the three patterns defined above provides more detail than other measures of overlap,
  % such as the proportion of one species' partners that are shared with
  % another as given by Jaccard similarity. In particular, comparing the probability of observing each pattern
  % rather than one of the other two provides a measure of indirect
  % interactions between plants by considering pairs of animal partners rather
  % than each animal separately. For example, a pair of plants which share 
  % two interaction partners are more likely to influence each other via these partners
  % than two plants which do not share interaction partners. Moreover, our measure
  % of overlap has greater statistical power than Jaccard dissimilarity because
  % it includes information on the \emph{number} of shared interaction partners as
  % well as the proportion. For instance, a pair of plants which together interact
  % with 100 animals provides more information about shared overlap than a pair of
  % plants which together interact with only one animal whereas the Jaccard similarity
  % of both would simply be one.

  % [[It appears we switched to Jaccard and Sorenson dissimilarities - number of shared partners and number of shared partners*2/notshared.]]

@@

  We modelled the relationship between niche overlap and phylogenetic distance
  using a logistic regression. We used both the numbers of shared and 
  non-shared partners as dependent variables and centred, scaled phylogenetic 
  distance as the independent variable. This is conceptually similar to 
  modelling successes and failures in a binomial-distributed process. 
  Accordingly, we assumed a binomial distribution for residuals. All regressions were fit using the R~\citep{R} function 
  ``glm'' from package \emph{lme4}~\citep{lme4}. To avoid potential 
  confounding effects of different relationships in different networks, we 
  modelled the relationship between overlap and phylogenetic distance within 
  each network separately.

  Note that pairs of plants are not always independent: the same plant will
  appear in many pairs. This violates the assumption of independence used when 
  calculating the significance of logistic regressions within the R~\citep{R} 
  package \emph{lme4}~\citep{lme4}. To calculate significance of the 
  relationships we observed, it was therefore necessary to compare the 
  observed relationships to those in a suite of random networks. To create 
  these networks, we shuffled interactions among species while preserving row 
  and column totals. That is, each species retained the same number of 
  interaction partners as in the observed network but the exact set of 
  partners (and therefore niche overlaps with all other species) varied across 
  random networks. We preserved the observed phylogenetic relationships 
  between species in all cases. For each observed network, we created 999 such 
  random networks and calculated the relationship between niche overlap and 
  phylogenetic distance. This gave us a null distribution for each observed 
  network with which to determine the significance of the observed 
  relationship.

  This randomization approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 randomizations of each 
  random network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of randomized networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the randomizations 
  of these random networks (type I error). [[How does this get at type II error?]]

  % To determine how overlap of interaction partners
  % breaks down over phylogenetic distance,
  % we modelled the probabilities of observing each pattern
  % of overlap relative to the other two patterns.
  % We expected that the frequency of the high- and moderate-overlap 
  % patterns would decrease with increasing phylogenetic distance
  % between two plants while the frequency of the low-overlap pattern would
  % increase. As we expect pollination and herbivory networks could 
  % show different patterns of overlap, we included effects of network 
  % type and the interaction between network type and distance. Lastly, to
  % account for the possibility that different communities show different
  % characteristic relationships, we also included random effects of network ID on the slope 
  % and intercept, giving a mixed-effects logistic regression of the form
  % \begin{equation}
  % logit(\omega_{pnij}) \propto \delta_{ij} + \rho_{n} + \delta_{ij}\rho_{n} + N_{n} + \delta_{ij}N_{n} ,
  % \label{networklevel}
  % \end{equation}

  % \noindent where $\omega_{pnij}$ is the probability of overlap pattern $p$ occurring between
  % species $i$ and $j$ in network $n$, $\delta_{ij}$ is the phylogenetic distance between 
  % plants $i$ and $j$, $\rho_{n}$ is the network type (one in pollination networks,
  % zero in herbivory networks), and $N_n$ and $\delta_{ij}N_{n}$ are random slope and intercepts 
  % for network $n$. All models were fit using R function glmer from package lme4~\citep{lme4}.
  % Sample size for these models was the sum (over all pairs of plants) of the number of pairs 
  % of animals where each plant and each animal has at least one interaction partner. Over all 
  % networks, there were 43,288,090 such sets of plants and animals, with a median of 72 (mean 
  % 671 +/- 2247) pairs of animals per pair of plants and median 58,528 (mean 636,590)
  % plant-animal sets per network.

@@

  Next, we examined the connection between our network-level observations
  and the plant families present in each community.
  Specifically, we tested the hypothesis that
  varying relationships between phylogenetic distance and
  pairwise niche overlap are due to the different distributions 
  of families across networks. To do this, we performed a non-parametric
  permutational multi-variate analysis of variance
  (PERMANOVA;~\citealp{Anderson2001}) using the change in log
  odds of two plants sharing an interaction partner to 
  predict the Bray-Curtis dissimilarity of networks
  based on the composition of their plant component
  (defined as the proportions of the plant community
  made up by each plant family present in the entire dataset).
  We used Bray-Curtis dissimilarity because, for a given
  pair of networks, only those plant families that appear
  in at least one network are considered~\citep{Anderson2001,Cirtwill2015}; 
  that is, the absence of rare plant families will not make 
  two networks appear more similar than they actually are.

  Note that a PERMANOVA does not assume that the data are 
  normally distributed, but rather compares the pseudo-$F$ 
  statistic calculated from the observed data to a null 
  distribution obtained by permuting the raw data. As 
  pollination and herbivory networks might have different
  community composition, we stratified these permutations
  by network type. That is, the change in log odds for a pollination
  network could only be exchanged for that of another pollination
  network. Stratifying the permutations in this way ensures that 
  the null distribution used to calculate the $P$-value is not 
  biased by including combinations of changes in log odds and 
  community composition that would not occur because of inherent 
  differences in the two network types (e.g., \emph{Pinaceae} 
  only appeared in herbivory networks and should not be assigned 
  to pollination networks). We used 9999 such stratified permutations 
  to obtain the null distribution and obtain a $P$-value.

  The PERMANOVA tests whether there is an association between
  community composition and network-level patterns but does not
  give any information on \emph{which} plant families have the
  greatest effects. To address this, we supplemented the 
  PERMANOVA with three constrained correspondence analyses (CCAs)
  which placed plant families along an axis representing the
  change in log odds of sharing an interaction partner.
  A correspondence 
  analysis (CA) is similar to other multivariate
  analyses such as principal components analysis in that it
  reduces multivariate data to a set of orthogonal axes. A
  subset of axes that explain the majority of variation in 
  the data can then be interpreted to elucidate trends that
  were difficult to interpret in the full multivariate space.
  A constrained correspondence analysis (CCA) creates an extra
  axis based on some constraint - in this case, the change in
  log odds of sharing an interaction partner.
